---
title: "US Production"
author: "Iori Guido"
date: "13 marzo 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Exploring the US production data

In this application it is possible to explore the data about the US production during years 1970-1986. We will focus about the production values about: 

- Highway and streets
- Water and sewer facilities
- Other public buildings and structures

The production values can be analyzed w.r.t the geography of US, indeed a GoogleVis map to show the data on a map, and w.r.t some economic indicators:

- Private capital stock
- Public capital
- State unemployment rate

## User interactions

The user can explore the date by choosing in the side bar panel:

- Production sector
- Economic indicator
- Year

In the main panel, the user can switch between 3 tabs:

- information about the data set
- the GoogleVis chart
- the plotly scatter-plot


## Example of Plolty output for 1970, Water vs. Public Capital

```{r cars, echo = FALSE, message=FALSE, warning=FALSE}
    library(shiny)
    library(plotly)
    library(ggplot2)
    library(googleVis)
    library(Ecdat)
    library(devtools)
    library(webshot)

    data(Produc)
    Produc$year <- as.factor(Produc$year)
    myData <- split(Produc, Produc$year)

    dx <- myData[[as.character("1970")]]["pc"] 
    dy <- myData[[as.character("1970")]]["water"] 
    ds <- myData[[as.character("1970")]]["state"]
    df <- data.frame(cbind(dx,dy,ds))
    
    #summary(df)
    fit <- lm( df[,1] ~df[,2], data = df)
    
    #print(summary(fit))
    xlab <- list(
      title = "pc"
    )
    
    ylab <- list(
      title = "water"
    )
    
    plot_ly( df, x= df[,1] , y= df[,2], text= df[,3], type="scatter", mode = "markers"  ) %>% 
      layout(xaxis = xlab, yaxis = ylab, showlegend = FALSE) %>% 
      add_trace(df, 
                x = df[,1],
                y = fitted(lm(df[,2] ~ df[,1])),
                mode = "lines",
                showlegend=FALSE
      )

    
```

## Tools used

In this application the following components explained during the lessons have been used:

- GoogleVis plot
- Plolty for the interactive scatter plot
- Slinder and select inputs in Shiny
- Side bar panel and main panel
- Tab panel to separate the map chart from the scatter plot chart and the presentation of the date set used.

Check the following links: [GitHub](https://giori.shinyapps.io/USProduction/) and the [Shiny App](https://giori.shinyapps.io/USProduction/). 






